Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2015-06-27 analysis/8-sim-extinction-risk.Rmd
Remove testing subset on filenames

<!--
I've picked parameter values to be approximately at the mean values in the GPDD (I'll check these more precisely). I'm running the simulation, by default, for 200 generations and discarding the first 50 as burn in.
-->

```{r}
# library("skewt")
sim_gomp_extinction <- function(abundance_ts, lambda = 1, b = 0.5, N = 100L,
  df = 3, thresh = 3, sigma = 0.2, id = 1, bootstrap_residuals = FALSE, 
  model = "heavy") {

@@

  if (bootstrap_residuals) {
    res <- log_abundance_ts[-1] - (lambda + b * log_abundance_ts[-length(abundance_ts)])
    proc_error <- sample(res, size = N, replace = TRUE) # bootstrap the process residuals
  } else {
    if (model == "heavy") {
      # proc_error <- rskt(N, df = df, gamma = gamma) / (1 / sigma)
      proc_error <- rt(N, df = df) * sigma
    } else {
      proc_error <- rnorm(N, sd = sigma)
    }
  }

@@

    y_return <- c(log_abundance_ts, y)
    generation <- c(seq(-length(abundance_ts) + 1, 0), seq_along(y))
    data.frame(b = b, N = N,
      df = df, sigma = sigma, thresh = thresh, lambda = lambda,
      n_ext = sum(exp(y) < thresh), mean_log_abund = mean(y),
      dat = y_return, generation = generation, main_id = id)
}
```

@@

```{r}
ids <- c(6528, 10127, 20579)
library("rstan")
gpdd <- readRDS("gpdd-clean.rds") # to get the last abundance
samples <- 2000L
posterior_length <- 2000L
posterior_ids <- round(seq(1, posterior_length, length.out = samples))

>>>>

```{r}
# library("skewt")
sim_gomp_extinction <- function(abundance_ts, lambda = 1, b = 0.5, N = 100L,
  nu = 3, log_skew = 1, sigma_proc = 0.2, id = 1, 
  bootstrap_residuals = FALSE, model = "heavy") {

@@

  if (bootstrap_residuals) {
    res <- log_abundance_ts[-1] - (lambda + b * log_abundance_ts[-length(abundance_ts)])
    proc_error <- sample(res, size = N, replace = TRUE) # bootstrap the process residuals
  } else {
    if (model == "heavy") {
      proc_error <- rskt(N, df = nu, gamma = exp(log_skew)) * sigma_proc
    } else {
      proc_error <- rnorm(N, sd = sigma_proc)
    }
  }

@@

    y_return <- c(log_abundance_ts, y)
    generation <- c(seq(-length(abundance_ts) + 1, 0), seq_along(y))
    data.frame(b = b, N = N,
      nu = nu, sigma = sigma_proc, thresh = thresh, lambda = lambda,
      skew = exp(log_skew), dat = y_return, generation = generation, 
      main_id = id)
}
```

@@

```{r}
ids <- c(6528, 10127, 20579)
library("rstan")
gpdd <- readRDS("gpdd-clean.rds") # to get the last abundance
